NumPy---Array Programming in Python

### 2020-01-11 body.tex
Flesh out caption for Fig. 1: Fundamental Array Concepts

\begin{figure*}
  \centering
  \includegraphics[width=\textwidth]{static/sketches/array-concepts}
  \caption{\textbf{Fundamental Array Concepts.}
    \textbf{a,} The NumPy array data structure ...
    \textbf{b,} Indexing ...
    \textbf{c,} Broadcasting ...
    \textbf{d,} Indexing with arrays ... combined with broadcasting ...
   }
  \label{fig:array-concepts}
\end{figure*}

>>>>

\begin{figure*}
  \centering
  \includegraphics[width=\textwidth]{static/sketches/array-concepts}
  \caption{\textbf{Fundamental Array Concepts.}
    \textbf{a,} The NumPy array data structure and its associated meta-data fields.
    \textbf{b,} Indexing an array with various types of arguments.
    \textbf{c,} Broadcasting in scalar addition, and in the division of two-dimensional arrays.
    \textbf{d,} Indexing with arrays, which broadcast the indexing arguments before performing the lookup.
   }
  \label{fig:array-concepts}
\end{figure*}
